### 2009-03-23 doc/a-rex/arex_tech_doc.tex
Fixing joboption names
Adding MigrateActivity documentation

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration (This feature
does not work in current implementation).
\end{itemize}
\end{itemize}

@@

A-REX introduces a new operation in addition to those provided by
BES. It does that by defining its own port-type with the single operation
\emph{ChangeActivityStatus} (see Appendix~\ref{annex:arex-wsdl}). This operation provides
a way to request simple transfers between states of jobs and corresponding
actions.

\begin{itemize}
\item \emph{ChangeActivityStatus}
\begin{itemize}
\item Input
\begin{itemize}
\item \emph{ActivityStatusType OldStatus}: Description of the state the
job is supposed to be in during execution of this request. If the
current state of the job is different from the one having been given,
the operation is aborted and a fault is returned. This parameter is
optional.
\item \emph{ActivityStatusType NewStatus}: Description of the state the
job is to be put into.
\end{itemize}
\item Output
\begin{itemize}
\item \emph{ActivityStatusType NewStatus}: Description of the current state
of the job.
\end{itemize}
\item Fault(s)
\begin{itemize}
\item \emph{NotAuthorizedFault}: Indicates that the client is not allowed
to do this operation.
\item \emph{InvalidActivityIdentifierFault}: There is no such job/activity.
\item \emph{CantApplyOperationToCurrentStateFault}: The requested transition
is not possible.
\end{itemize}
\end{itemize}
\end{itemize}

@@

@@

\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{\emph{IsExecutable}}] -- marks file to become executable
after being delivered to the computing resource.
\item [{\emph{RunTimeEnvironment}}] -- specifies the name of the Runtime
Environment needed for job execution.
\item [{\emph{Middleware}}] -- request for specific middleware on the computing
resource frontend.
\item [{\emph{RemoteLogging}}] -- destination for the usage record
report of the executed job.
\item [{\emph{LocalLogging}}] -- name for the virtual directory available
through job interface and containing various debug information about
job execution.
\item [{\emph{AccessControl}}] -- ACL expression which describes the identities
of those clients who are allowed to perform operations on this job.
\item [{\emph{Notify}}] -- Email destination for notification of job state
changes.
\item [{\emph{SessionLifeTime}}] -- duration for the directory containing
job-related files to exist after the job finished executing.
\item [{\emph{JoinOutputs}}] -- specifies if standard output and standard
error channels must be merged.
\item [{\emph{Reruns}}] -- defines how many times a job is allowed
to rerun in case of failure.
\item [{\emph{CredentialServer}}] -- URL of MyProxy service which
may be used for renewing the expired delegated job credentials.
\item [{\emph{CandidateTarget}}] -- specifies host name and queue
of a computing resource.
\end{list}

@@

\begin{itemize}
\item joboption\_directory -- session directory.
\item joboption\_arg\_\# -- command with arguments to be executed as specified
in the JD (\textbf{not} bash array).
\item joboption\_env\_\# -- array of 'NAME=VALUE' environment variables (\textbf{not}
bash array).
\item joboption\_runtime\_\# -- array of requested \emph{runtimeenvironment}
names (\textbf{not} bash array).
\item joboption\_num -- \emph{runtimeenvironment} currently beeing processed
(number starting from 0).
\item joboption\_stdin -- name of file to be attached to stdin handle.
\item joboption\_stdout -- same for stdout.
\item joboption\_stderr -- same for stderr.
\item joboption\_maxcputime -- amount of CPU time requested (minutes).
\item joboption\_maxmemory -- amount of memory requested (megabytes).
\item joboption\_count -- number of processors requested.
\item joboption\_lrms -- LRMS to be used to run job.
\item joboption\_queue -- name of a queue of LRMS to put job into.
\item joboption\_nodeproperty\_\# -- array of properties of computing nodes
(LRMS specific, \textbf{not} bash array).
\item joboption\_jobname -- name of the job as given by user.
\item joboption\_rsl -- whole RSL for very clever submission scripts.
\item joboption\_rsl\_\emph{name} -- RSL attributes and values (like joboption\_rsl\_executable=''/bin/echo'')
\end{itemize}

@@

  <wsdl:message name=\char`\"{}ChangeActivityStatusRequest\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusRequest\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatus\char`\"{}/>
  <wsdl:message name=\char`\"{}ChangeActivityStatusResponse\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusResponse\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatusResponse\char`\"{}/>

@@

@@

>>>>

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration (This feature
does not work in current implementation).
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persists if the termination of the previous 
job fails.
\end{itemize}
\end{itemize}

@@

A-REX introduces two new operations in addition to those provided by
BES. It does that by defining its own port-type with new operations
\emph{ChangeActivityStatus} and \emph{MigrateActivity}(see 
Appendix~\ref{annex:arex-wsdl}).

The \emph{ChangeActivityStatus} operation provides a way to request 
simple transfers between states of jobs and corresponding
actions.

\begin{itemize}
\item \emph{ChangeActivityStatus}
\begin{itemize}
\item Input
\begin{itemize}
\item \emph{ActivityStatusType OldStatus}: Description of the state the
job is supposed to be in during execution of this request. If the
current state of the job is different from the one having been given,
the operation is aborted and a fault is returned. This parameter is
optional.
\item \emph{ActivityStatusType NewStatus}: Description of the state the
job is to be put into.
\end{itemize}
\item Output
\begin{itemize}
\item \emph{ActivityStatusType NewStatus}: Description of the current state
of the job.
\end{itemize}
\item Fault(s)
\begin{itemize}
\item \emph{NotAuthorizedFault}: Indicates that the client is not allowed
to do this operation.
\item \emph{InvalidActivityIdentifierFault}: There is no such job/activity.
\item \emph{CantApplyOperationToCurrentStateFault}: The requested transition
is not possible.
\end{itemize}
\end{itemize}

@@

The \emph{MigrateActivity} operation generates a request to migrate a 
grid job from another ARC1 cluster, i.e. the operation will get input 
files and possibly job description from the cluster currently holding 
the job and create the job as a new activity at the present cluster.
Currently only migration of queuing jobs is supported.

\item \emph{MigrateActivity}
\begin{itemize}
\item Input
\begin{itemize}
\item \emph{wsa:EndpointReferenceType ActivityIdentifier}: This 
element should contain the \emph{wsa:EndpointReference} of the job to 
be migrated.
\item \emph{ActivityDocument}: JSDL document of the job to be 
migrated. This element is optional.
\item \emph{Boolean ForceMigration}: Boolean that determines whether 
the job will persist on the new cluster if the termination of the 
previous job fails.
\end{itemize}
\item Output
\begin{itemize}
\item \emph{wsa:EndpointReferenceType ActivityIdentifier}: This 
element should contain the \emph{wsa:EndpointReference} of the new 
activity.
\item \emph{ActivityDocument}: Contains the JSDL document of the new 
activity.
\end{itemize}
\item Fault(s)
\begin{itemize}
\item \emph{NotAuthorizedFault}: Indicates that the client is not allowed
to do this operation.
\item \emph{NotAcceptingNewActivitiesFault}: A fault that indicates that A-REX 
currently is not accepting new activities.
\item \emph{UnsupportedFeatureFault}: This fault indicates that an sub-element in the 
JDSL document is not supported or the ActivityDocument has not been recognised as JSDL. 
\item \emph{InvalidRequestMessageFault}: This fault indicates that an element in the 
request is either missing or has an invalid format. Typically this would mean that 
the job-id cannot be located in the ActivityIdentifier of the old job.
\end{itemize}
\end{itemize}
\end{itemize}

The \emph{ActiviterIdentifier} specifies the URL of the job which will be migrated. In case the 
\emph{ActivityDocument} is filled this document will be used to create a new activity otherwise 
an attempt will be made to retrieve the job description through the BES operation
\emph{GetActivityDocument}.

Once the input files have been downloaded from the other cluster, a request will be send 
to terminate the old job. If this request fails the new activity at the present cluster 
will be terminate unless the \emph{ForceMigration} is true. This is to prevent the job 
from being executed at two different places at the same time.

@@

\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item [{\emph{IsExecutable}}] -- marks file to become executable
after being delivered to the computing resource.
\item [{\emph{RunTimeEnvironment}}] -- specifies the name of the Runtime
Environment needed for job execution.
\item [{\emph{Middleware}}] -- request for specific middleware on the computing
resource frontend.
\item [{\emph{RemoteLogging}}] -- destination for the usage record
report of the executed job.
\item [{\emph{LocalLogging}}] -- name for the virtual directory available
through job interface and containing various debug information about
job execution.
\item [{\emph{AccessControl}}] -- ACL expression which describes the identities
of those clients who are allowed to perform operations on this job.
\item [{\emph{Notify}}] -- Email destination for notification of job state
changes.
\item [{\emph{SessionLifeTime}}] -- duration for the directory containing
job-related files to exist after the job finished executing.
\item [{\emph{JoinOutputs}}] -- specifies if standard output and standard
error channels must be merged.
\item [{\emph{Reruns}}] -- defines how many times a job is allowed
to rerun in case of failure.
\item [{\emph{CredentialServer}}] -- URL of MyProxy service which
may be used for renewing the expired delegated job credentials.
\item [{\emph{CandidateTarget}}] -- specifies host name and queue
of a computing resource.
\item [{\emph{OldJobID}}] -- specifies the previous job-ids in case the job 
has been resubmitted or migrated.
\end{list}

@@

\begin{itemize}
\item joboption\_directory -- session directory.
\item joboption\_arg\_\# -- command with arguments to be executed as specified
in the JD (\textbf{not} bash array).
\item joboption\_env\_\# -- array of 'NAME=VALUE' environment variables (\textbf{not}
bash array).
\item joboption\_runtime\_\# -- array of requested \emph{runtimeenvironment}
names (\textbf{not} bash array).
\item joboption\_num -- \emph{runtimeenvironment} currently beeing processed
(number starting from 0).
\item joboption\_stdin -- name of file to be attached to stdin handle.
\item joboption\_stdout -- same for stdout.
\item joboption\_stderr -- same for stderr.
\item joboption\_cputime -- amount of CPU time requested (minutes).
\item joboption\_memory -- amount of memory requested (megabytes).
\item joboption\_count -- number of processors requested.
\item joboption\_lrms -- LRMS to be used to run job.
\item joboption\_queue -- name of a queue of LRMS to put job into.
\item joboption\_nodeproperty\_\# -- array of properties of computing nodes
(LRMS specific, \textbf{not} bash array).
\item joboption\_jobname -- name of the job as given by user.
\item joboption\_rsl -- whole RSL for very clever submission scripts.
\item joboption\_rsl\_\emph{name} -- RSL attributes and values (like joboption\_rsl\_executable=''/bin/echo'')
\end{itemize}

@@

      <xsd:complexType name="MigrateActivityType">
	  	           type=\char`\"{}wsa:EndpointReferenceType\char`\"{} 
	  	           minOccurs=\char`\"{}1\char`\"{} maxOccurs=\char`\"{}1\char`\"{}/>
          <xsd:element ref=\char`\"{}bes-factory:ActivityDocument\char`\"{} minOccurs=\char`\"{}0\char`\"{}/>
	  <xsd:element name=\char`\"{}ForceMigration\char`\"{} type=\char`\"{}xsd:boolean\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}1\char`\"{}/>    
          <xsd:any namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}unbounded\char`\"{}/>        
        <xsd:anyAttribute namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{}/>

      <xsd:complexType name=\char`\"{}MigrateActivityResponseType\char`\"{}>
        <xsd:sequence>
          <xsd:element name=\char`\"{}ActivityIdentifier\char`\"{} type=\char`\"{}wsa:EndpointReferenceType\char`\"{}/>
          <xsd:element ref=\char`\"{}bes-factory:ActivityDocument\char`\"{} minOccurs=\char`\"{}0\char`\"{}/>
          <xsd:any namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{} minOccurs=\char`\"{}0\char`\"{} maxOccurs=\char`\"{}unbounded\char`\"{}/>        
        </xsd:sequence>
        <xsd:anyAttribute namespace=\char`\"{}##other\char`\"{} processContents=\char`\"{}lax\char`\"{}/>
      </xsd:complexType>

      <xsd:element name=\char`\"{}MigrateActivity\char`\"{}
        type=\char`\"{}a-rex:MigrateActivityType\char`\"{}/>
      <xsd:element name=\char`\"{}MigrateActivityResponse\char`\"{}
        type=\char`\"{}a-rex:MigrateActivityResponseType\char`\"{}/>

    </xsd:schema>
  </wsdl:types>
  <wsdl:message name=\char`\"{}ChangeActivityStatusRequest\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusRequest\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatus\char`\"{}/>
  </wsdl:message>
  <wsdl:message name=\char`\"{}ChangeActivityStatusResponse\char`\"{}>
    <wsdl:part name=\char`\"{}ChangeActivityStatusResponse\char`\"{}
               element=\char`\"{}a-rex:ChangeActivityStatusResponse\char`\"{}/>
  </wsdl:message>

  <wsdl:message name=\char`\"{}MigrateActivityRequest\char`\"{}>
    <wsdl:part name=\char`\"{}MigrateActivityRequest\char`\"{} 
	element=\char`\"{}a-rex:MigrateActivity\char`\"{}/>
  </wsdl:message>

  <wsdl:message name=\char`\"{}MigrateActivityResponse\char`\"{}>
    <wsdl:part name=\char`\"{}MigrateActivityResponse\char`\"{} 
        element=\char`\"{}a-rex:MigrateActivityResponse\char`\"{}/>
  </wsdl:message>

@@

    <wsdl:operation name=\char`\"{}MigrateActivity\char`\"{}>
      <wsdl:input 
         name=\char`\"{}MigrateActivity\char`\"{}
         message=\char`\"{}a-rex:MigrateActivityRequest\char`\"{}  
      <wsdl:output
         name=\char`\"{}MigrateActivityResponse\char`\"{}
         message=\char`\"{}a-rex:MigrateActivityResponse\char`\"{}
      <wsdl:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{} 
         message=\char`\"{}bes-factory:NotAcceptingNewActivitiesFault\char`\"{}
      <wsdl:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{} 
         message=\char`\"{}bes-factory:UnsupportedFeatureFault\char`\"{}
      <wsdl:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{}
         message=\char`\"{}bes-factory:InvalidRequestMessageFault\char`\"{}

@@

    <wsdl:operation name=\char`\"{}MigrateActivity\char`\"{}>
      <soap:operation soapAction=\char`\"{}MigrateActivity\char`\"{} /> 
      <wsdl:input name=\char`\"{}MigrateActivity\char`\"{}>
        <soap:body use=\char`\"{}literal\char`\"{} />
      <wsdl:output name=\char`\"{}MigrateActivityResponse\char`\"{}>
        <soap:body use=\char`\"{}literal\char`\"{} />
      <wsdl:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{}>
        <soap:fault name=\char`\"{}NotAcceptingNewActivitiesFault\char`\"{} use=\char`\"{}literal\char`\"{} />
      <wsdl:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{}>
        <soap:fault name=\char`\"{}UnsupportedFeatureFault\char`\"{} use=\char`\"{}literal\char`\"{} />
      <wsdl:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{}>
        <soap:fault name=\char`\"{}InvalidRequestMessageFault\char`\"{} use=\char`\"{}literal\char`\"{} />
